### 2021-07-16 ch/2-related-work.tex
Tick off another two requests

>>>>

\subsection{Balancing datasets with synthetic data}
Another way to view the fairness problem is to regard the dataset as missing certain kinds of samples.
This falls under the ground-truth-centric view:
the \emph{true} data distribution is fair, but our training set only covers a part of it,
which means it looks unbalanced or unfair.
An idea to deal with this, is to \emph{generate} the missing data,
typically with a \ac{GAN}.

\citet{sattigeri2019fairness} is one such approach.
The method is based on a conditional \ac{GAN},
that is conditioned on the sensitive attribute \(s\).
The \ac{GAN} then produces fake input samples \(x_F\) together with corresponding labels \(y_F\).
In addition to the usual discriminator which tries to distinguish fake \(x_F\) from real \(x\) samples,
there is another adversary that tries to predict \(s\) from \(y_F\),
which is opposed by the generator.
This is meant to ensure that the labels of the generated samples
have the same distribution for all values of \(s\),
\ie, that the generated data distribution is balanced in terms of \(s\) and \(y\).
There is also a discriminator that takes both \(x_F\) and \(y_F\) as inputs,
and determines whether this is a plausible pair.
Once this \ac{GAN} has been trained,
a classifier is trained on the generated, balanced data.
The expected advantage over other methods of balancing the dataset is
that this method produces a more realistic distribution,
because the adversarial training ensures that the data ``looks real''.
However, this reliance on the discriminator also means
that the generated data cannot contain data from unobserved parts of the data distribution,
because such data would very easily be spotted as fake.
For example, if a face image dataset does not contain men with lipstick,
then the \ac{GAN} will also not produce such samples
(even though it knows about men and it knows about lipstick).
Generally, \acp{GAN} cannot produce something out of nothing,
so if the data is missing certain sectors entirely,
it is very hard to produce samples from this sector that are \emph{realistic}.
This problem can potentially be ameliorated by pretraining the \ac{GAN}
on diverse, unlabelled data.

### 2021-07-16 ch/7-discussion.tex
Tick off another two requests

@@

% ======== something something adversarial examples ========
% ==============

% ======== what can we do if we don't know there is a bias? ========
% ==============

@@

>>>>

% ======== data augmentation ========
A topic that was left out of the thesis is \emph{data augmentation},
which refers to the practice of modifying copies of the samples in the training set
with pre-defined transformations, which do not change the ``semantic content'',
such that more samples are available for training.
For image data, typical transformations are rotations, crops, mirroring, Gaussian noise, and slight colour modifications.
If chosen right, data augmentation alone can solve the problems presented in this thesis:
grey-scaling is a transformation that is sometimes used for image data,
and works quite well on the Coloured MNIST problem
(though not perfectly well, because even as shades of grey, the colours are distinguishable).
However, this only works because the spurious feature is so simply here
(after all, Coloured MNIST is mostly intended to be a simple toy dataset).
Grey-scaling would not help with real-world datasets like CelebA.
Furthermore, even if a simple transformation would be able to remove the spurious feature,
knowing \emph{which} transformation will accomplish this is not always as obvious as with Coloured MNIST,
and may require special domain knowledge (like signal processing for audio data).
Thus, the goal for the presented methods here was to make them applicable do any kind of data,
without requiring knowledge of the specific details of how the bias manifests itself in the data,
and without requiring knowledge of which data augmentations can be applied.
However, this is not a recommendation \emph{against} data augmentations;
if you have reason to believe that augmentations will help,
there is no reason not to use them.
% ==============

@@

@@

% ======== what can we do if we don't know there is a bias? ========
Another element that is currently missing is a way to determine
whether a given dataset has a bias,
in cases where you do not know enough about the data to know where to look.
This runs into very similar problems to the ones discussed above:
how can the algorithm know what counts as a bias?
(use GPT to find out?)
% ==============
